\section{Model Calibration}
We calibrated the Sri Lanka national model to two targets: case notifications and infection-related deaths. Further details on the calibration procedure are described below and the prior distributions of epidemiological calibration parameters are described in (Table \ref{tab:calibration_params}). 

\subsection{General approach}
The model was calibrated using an adaptive Metropolis (AM) algorithm. In particular, we used the algorithm
based on adaptive Gaussian proposal functions proposed by Haario et al. to sample parameters from
their posterior distributions. We ran seven independent AM chains and combined the samples of the
seven chains to project epidemic trajectories over time. The definitions of the prior distributions and the
likelihood are detailed as follows.

\subsection{Likelihood function}
Likelihood functions are derived from comparing model outputs to target data at each time point nominated
for calibration. The dispersion parameters of these distribution are included as calibration parameters and
varied during the calibration approach to improve calibration efficiency.

\subsection{Calibration parameters}
Epidemiological calibration parameters are described in (Table \ref{tab:calibration_params}). 
\vspace{-24mm}
\begin{table}[htp]

    \begin{tabular}{| p{4.4cm} | p{4.4cm} | p{5cm} |}
        \hline
        \textbf{Parameter name} & \textbf{Distribution type} & \textbf{Distribution Parameters} \\
        \hline
        Incubation period & Truncated normal & Mean 5.5 days, standard 			        deviation 0.97 days, truncation \textless 1 day \\
      \hline
      Infectious period (for clinical strata 1 to 3) & Truncated normal &         	  Mean 6.5 days, standard deviation 0.77 days, truncation \textless 4 		      days \\
      \hline
      Risk of infection per contact & Uniform & 0.018 to 0.028\\
      \hline
      Infectious seed & Uniform & Range 150 to 400 \\
      \hline
   	  Case detection rate at testing rate of 1 test per 10, 000 per day 		      (proportion) & Uniform 	      & Range 0.04 to 0.18 \\
   	  \hline
   	  Increased transmissibility of VoC strains  & Uniform & 1.5 to 3.0\\
      \hline
      Start time of VoC emergence  & Uniform & Jan 14, 2021 to Mar 15, 2021 \\
      \hline
    \end{tabular}
    \caption{Epidemiological calibration parameters}
    \label{tab:calibration_params}
\end{table}
\clearpage
