\section{Model calibration and uncertainty propagation}
\label{calibration}
\textcolor{red}{REVISE THE SECTION BELOW WHEN FINALISED}
The model was calibrated using a Bayesian approach. In particular, we used the adaptive 
Metropolis algorithm introduced by Haario \textit{et al.} to sample parameters from their 
posterior distributions \cite{haario-2001}. For each country, we ran 8 independent Metropolis 
chains initialised using Latin Hypercube Sampling based on the parameter priors. 
We ran simulations for 1 hour per chain yielding at least 60,000 iterations per 
chain. We discarded the first 30,000 iterations of each chain as burn-in and combined the 
samples of the 8 chains to project epidemic trajectories over time. 
For each modelled country, the epidemic projections presented in our analysis are associated with 1000 parameter sets 
randomly sampled from the posterior distributions obtained from MCMC sampling. 
The definitions of the prior distributions and the likelihood are detailed in the following sections.

\subsection{Parameters varied during calibration}

The parameters varied during calibration along with their associated prior distributions 
are listed in Table (\textcolor{red}{add ref to table here}) and indicated with the superscript \textsuperscript{c}.
We used uniform prior distributions for all calibrated parameters. The primary parameters varied during calibration are 
the unadjusted risk of transmission per contact ($\beta$), the IFR multiplier ($m_C$), the infection seeding times of 
each strain and the proportion of students on-site during ``Partially open'' periods. Note that the values of the random 
process $W_t$ described in Section \ref{random_process} are also treated like calibrated parameters by the MCMC. The Gaussian 
auto-regressive component described in Equation \ref{eq:random_process} is incorporated in the posterior likelihood 
computation (Section \ref{likelihood}).

\subsection{Calibration targets}
\label{targets}
Model calibration is performed independently for each country. All models are fitted to the reported number of COVID-19 deaths over time.
We used the daily number of COVID-19 deaths reported by Our World in Data and applied a 7-day moving average to the observed data. 

In addition, for countries where a nationally representative seroprevalence survey had been conducted (n=39), we include
seroprevalence data in the calibration likelihood. We used the online platform SeroTracker to extract country-specific seroprevalence estimates.

\textcolor{red}{Use Angus' description here.}
\textcolor{red}{Also mention how we match age-specific estimates in the model}

\begin{table}[!ht]  
    \footnotesize
    \begin{center}
        \begin{tabular}{p{2cm} | p{1.6cm} | p{1.6cm} | p{0.8cm} | p{0.8cm} | p{1cm} | p{1.3cm} | p{1.2cm} | p{1.2cm}}
           \hline            
           
           \textbf{country} & \textbf{sampling start date} & \textbf{sampling end date} & \textbf{age min} & \textbf{age max} & \textbf{denom. value} & \textbf{serum pos prevalence} & \textbf{estimate grade} & \textbf{overall risk of bias} \\ 
\hline 
\href{https://dx.doi.org/10.5694/mja2.51542}{\textcolor{blue}{Australia}} & 2020-11-03 & 2021-03-12 &  & 19 & 1685 & 0.0023 & National & High \\ 
\hline 
\href{https://dx.doi.org/10.1007/s15010-021-01639-0}{\textcolor{blue}{Austria}} & 2020-06-05 & 2020-12-04 & 18 & 72 & 20228 & 0.025 & National & High \\ 
\hline 
\href{https://dx.doi.org/10.1371/journal.pone.0268093}{\textcolor{blue}{Bangladesh}} & 2020-10-15 & 2021-02-15 & 10 &  & 3220 & 0.673 & National & Moderate \\ 
\hline 
\href{https://dx.doi.org/10.2807/1560-7917.ES.2022.27.9.2100419}{\textcolor{blue}{Belgium}} & 2020-05-18 & 2020-05-25 &  & 101 & 3242 & 0.062 & National & Low \\ 
\hline 
\href{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC8225319/}{\textcolor{blue}{Brazil}} & 2020-05-14 & 2020-06-23 &  &  & 89362 & 0.023 & National & Moderate \\ 
\hline 
\href{http://dx.doi.org/10.1111/trf.16296}{\textcolor{blue}{Canada}} & 2020-05-09 & 2020-07-21 & 17 &  & 74642 & 0.007 & National & Moderate \\ 
\hline 
\href{https://dx.doi.org/10.1186/s12879-022-07045-7}{\textcolor{blue}{Chile}} & 2020-09-25 & 2020-11-25 & 7 & 94 & 2493 & 0.104 & National & Low \\ 
\hline 
\href{https://dx.doi.org/10.1016/j.lana.2022.100195}{\textcolor{blue}{Colombia}} & 2020-09-21 & 2020-12-11 & 5 & 80 & 17863 & 0.3253 & National & Moderate \\ 
\hline 
\href{https://dx.doi.org/10.3390/pathogens10060774}{\textcolor{blue}{Croatia}} & 2020-12-15 & 2021-02-15 &  &  & 1436 & 0.251 & National & High \\ 
\hline 
\href{https://doi.org/10.1038/s43856-022-00080-0}{\textcolor{blue}{Czechia}} & 2021-02-01 & 2021-03-31 & 18 &  & 19548 & 0.51 & National & High \\ 
\hline 
\href{https://dx.doi.org/10.1007/s10654-021-00796-8}{\textcolor{blue}{Denmark}} & 2020-08-15 & 2020-09-30 & 12 &  & 11478 & 0.02 & National & Low \\ 
\hline 
\href{https://dx.doi.org/10.3389/fmed.2022.933260}{\textcolor{blue}{Ecuador}} & 2020-10-12 & 2020-10-19 &  &  & 1250 & 0.1168 & National & Moderate \\ 
\hline 
\href{https://dx.doi.org/10.1080/23744235.2021.1974540}{\textcolor{blue}{Estonia}} & 2021-02-08 & 2021-03-25 &  &  & 2517 & 0.201 & National & High \\ 
\hline 
\href{http://dx.doi.org/10.1016/j.ijid.2021.08.028}{\textcolor{blue}{Ethiopia}} & 2020-06-24 & 2020-07-08 & 15 &  & 16932 & 0.035 & National & Low \\ 
\hline 
\href{https://dx.doi.org/10.1038/s41467-021-23233-6}{\textcolor{blue}{France}} & 2020-05-11 & 2020-05-17 &  &  & 3592 & 0.0493 & National & Low \\ 
\hline 
\href{https://revistas.ucr.ac.cr/index.php/psm/article/view/43261/46175}{\textcolor{blue}{Honduras}} & 2020-06-16 & 2020-06-23 & 5 &  & 792 & 0.062 & National & Moderate \\ 
\hline 
\href{https://dx.doi.org/10.1007/s11357-020-00226-9}{\textcolor{blue}{Hungary}} & 2020-05-01 & 2020-05-16 & 14 &  & 10474 & 0.0068 & National & Low \\ 
\hline 
\href{http://dx.doi.org/10.1016/j.cmi.2021.06.002}{\textcolor{blue}{Iran}} & 2020-08-03 & 2020-10-31 & 6 & 109 & 11256 & 0.142 & National & Low \\ 
\hline 
\href{https://dx.doi.org/10.1007/s10654-021-00749-1}{\textcolor{blue}{Israel}} & 2020-06-28 & 2020-09-14 &  &  & 54357 & 0.046 & National & Moderate \\ 
\hline 
\href{https://www.istat.it/it/files//2020/08/ReportPrimiRisultatiIndagineSiero.pdf}{\textcolor{blue}{Italy}} & 2020-05-25 & 2020-07-15 &  &  & 64660 & 0.025 & National & Moderate \\ 
\hline 
\href{https://dx.doi.org/10.3201/eid2702.204088}{\textcolor{blue}{Japan}} & 2020-06-01 & 2020-06-07 & 20 &  & 7950 & 0.001 & National & Moderate \\ 
\hline 
\href{http://dx.doi.org/10.1016/j.onehlt.2021.100292}{\textcolor{blue}{Jordan}} & 2020-10-01 & 2020-10-31 &  &  & 5470 & 0.07 & National & Moderate \\ 
\hline 
\href{https://dx.doi.org/10.1001/jama.2021.15265}{\textcolor{blue}{Kenya}} & 2021-01-03 & 2021-03-15 & 16 & 64 & 3018 & 0.485 & National & Moderate \\ 
\hline 
\href{https://dx.doi.org/10.1186/s12879-022-07031-z}{\textcolor{blue}{Lebanon}} & 2020-12-07 & 2021-01-15 &  &  & 2058 & 0.185 & National & Low \\ 
\hline 
\href{https://www.journals.vu.lt/AML/article/view/22344}{\textcolor{blue}{Lithuania}} & 2020-08-10 & 2020-09-10 & 18 & 92 & 3089 & 0.014 & National & Moderate \\ 
\hline 
\href{https://dx.doi.org/10.3201/eid2813.212348}{\textcolor{blue}{Malawi}} & 2020-10-14 & 2020-12-08 &  &  & 4261 & 0.078 & National & Low \\ 
\hline 
\href{https://dx.doi.org/10.1016/j.lanwpc.2021.100317}{\textcolor{blue}{Mongolia}} & 2020-10-13 & 2020-12-04 &  &  & 5000 & 0.0136 & National & Low \\ 
\hline 
\href{https://mohp.gov.np/attachments/article/708/First%20Sero-prevalence\_final\_report\_04-04-2021.pdf}{\textcolor{blue}{Nepal}} & 2020-10-09 & 2020-10-22 &  &  & 3040 & 0.144 & National & Low \\ 
\hline 
\href{https://dx.doi.org/10.1111/irv.12932}{\textcolor{blue}{Norway}} & 2020-12-27 & 2021-02-13 &  &  & 1912 & 0.032 & National & Moderate \\ 
\hline 
\href{https://dx.doi.org/10.1016/j.ijid.2021.09.062}{\textcolor{blue}{Oman}} & 2020-09-13 & 2020-09-24 & 5 &  & 4780 & 0.164 & National & Moderate \\ 
\hline 
\href{https://dx.doi.org/10.1007/s15010-021-01629-2}{\textcolor{blue}{Pakistan}} & 2020-07-15 & 2020-07-31 &  &  & 15390 & 0.424 & National & Moderate \\ 
\hline 
\href{https://europepmc.org/article/PPR/PPR359402}{\textcolor{blue}{Portugal}} & 2021-03-01 & 2021-03-17 &  &  & 2435 & 0.173 & National & Low \\ 
\hline 
\href{https://papers.ssrn.com/sol3/papers.cfm?abstract\_id=3826194}{\textcolor{blue}{Singapore}} & 2020-11-15 & 2020-12-15 & 23 & 83 & 937 & 0.0016 & National & High \\ 
\hline 
\href{https://dx.doi.org/10.1016/j.cmi.2021.03.009}{\textcolor{blue}{Slovenia}} & 2020-10-17 & 2020-11-10 &  & 99 & 1211 & 0.0429 & National & Low \\ 
\hline 
\href{https://dx.doi.org/10.1093/cid/ciac198}{\textcolor{blue}{South Africa}} & 2020-11-15 & 2021-04-15 &  &  & 7577 & 0.4523 & National & Moderate \\ 
\hline 
\href{https://bmjopen.bmj.com/content/11/4/e049837.abstract}{\textcolor{blue}{Rep. of Korea}} & 2020-09-24 & 2020-12-09 & 18 & 86 & 4085 & 0.0039 & National & Moderate \\ 
\hline 
\href{https://www.mscbs.gob.es/ciudadanos/ene-covid/docs/ESTUDIO\_ENE-COVID19\_INFORME\_FINAL.pdf}{\textcolor{blue}{Spain}} & 2020-06-08 & 2020-06-22 &  &  & 62167 & 0.052 & National & Low \\ 
\hline 
\href{https://www.folkhalsomyndigheten.se/contentassets/376f9021a4c84da08de18ac597284f0c/pavisning-antikroppar-genomgangen-covid-19-blodgivare-delrapport-2.pdf}{\textcolor{blue}{Sweden}} & 2020-11-23 & 2020-12-04 &  &  & 3183 & 0.07 & National & Moderate \\ 
\hline 
\href{https://www.thelancet.com/journals/langlo/article/PIIS2214-109X(21)00053-X/fulltext}{\textcolor{blue}{Zambia}} & 2020-07-04 & 2020-07-27 &  &  & 2704 & 0.021 & National & Low \\ 
\hline 

    \end{tabular}
    \end{center}
    \caption{Seroprevalence data extracted from SeroTracker (national surveys).}
    \label{tab:sero_national}
\end{table}


\subsection{Likelihood definition}
\label{likelihood}
Let $d_w$ denote the rounded average daily number of COVID-19 deaths during week $w$, and $\hat{d_w}^\theta$ 
the associated predicted number of deaths according to the model with parameter set $\theta$. 

For countries with seroprevalence data, let us denote $m$ the sample size associated with the seroprevalence survey selected from SeroTracker (Section \ref{targets}), 
and $k$ the number of seropositive individuals observed in the survey.
Let $\hat{\pi}^\theta$ denote the modelled age-matched proportion ever infected by the time the survey was conducted (using midpoint date) 
associated with the parameter set $\theta$. 
The likelihood was defined as follows for coutnries with seroprevalence data:

\begin{equation}
    \label{eq:likelihood}
    \mathcal{L}(\theta) := f_{m,\hat{\pi}^\theta}(k) \times \prod_w g_r(d_w | \:\hat{d_w}^\theta) \quad ,
\end{equation}
where $f_{n,p}(.)$ is the probability mass function of a binomial distribution $\mathcal{B}(n,p)$, and 
$g_r(. | \mu)$ is the probability mass function of a negative binomial distribution with mean $\mu$ and 
overdispersion parameter $r$. The parameter $r$ is automatically estimated by the MCMC algorithm.

For countries without seroprevalence data, the likelihood equation is reduced to:
\begin{equation}
    \label{eq:likelihood_nosero}
    \mathcal{L}(\theta) := \prod_w g_r(d_w | \:\hat{d_w}^\theta) \quad.
\end{equation}

The likelihood described above represents the goodness of fit of a particular model parameterisation with regards to the targeted data. 
This quantity needs to be adjusted for the prior likelihood of the parameter set in order to compute the MCMC acceptance quantity $\mathcal{Q}(\theta)$.
As we used uniform priors for all the parameters, the inclusion of the individual parameters' priors in the acceptance quantity is not necessary. 
Indeed, their respective contributions would cancel out as the same quantity would appear in the numerator and the denominator of the 
MCMC acceptance quantity ratio. However, the auto-regressive relationship described in Equation \ref{eq:random_process}
must be accounted for as part of the combined prior likelihood of a parameter set. This is what prevents unrealistic fluctuations of the random process.
If $W^\theta$ represents the random process associated with the parameter set $\theta$, the overall MCMC acceptance quantity is obtained by:

\begin{equation}
    \label{eq:acc_qtt}
    \begin{split}
    \mathcal{Q}(\theta) & = \mathcal{L}(\theta) \times \prod_{i=1}^{n} z_{W^\theta_{i-1},\sigma}(W^\theta_i) \\
                        & = f_{m,\hat{\pi}^\theta}(k) \times \prod_w g_r(d_w | \:\hat{d_w}^\theta) \times \prod_{i=1}^{n} z_{W^\theta_{i-1},\sigma}(W^\theta_i) \quad ,
    \end{split}
\end{equation}
where $z_{\mu,\sigma}(.)$ represents the probability density function of the normal distribution $\mathcal{N}(\mu, \sigma)$, and $n$ is the number 
of random process updates. The standard deviation $\sigma$ is automatically estimated by the MCMC.

\subsection{Software implementation}
\input{../../tex_descriptions/models/sm_covid/runtime.tex}
